### 2023-04-12 application.tex
details

\begin{proof}
Recall that resilience is equivalent to  $\Bad \subseteq \pred^*(\Safe)$. For every pushdown automaton $A=(Q,\Sigma,...)$ and every regular language $L \subseteq Q \times \Sigma^*$, the set $\pred^*(L)$ is a computable regular language \cite{DBLP:journals/ipl/BouajjaniEFMRWW00}. Since $\Bad$ and $\Safe$ are both regular, we deduce that
%
%			Moreover, $post^*(\Bad)$ is also a computable regular language \alain{pourquoi ?}   $post^*(L)$ and
 the inclusion $\Bad \subseteq \pred^*(\Safe)$ is decidable and resilience too.
%
The BRP and the kRP are also decidable. The algorithm that computes $ \pred^*(\Safe)$ is polynomial. If $\Bad \subseteq \pred^*(\Safe)$ then one computes an integer $k$ such that the maximum of all minimal pathes that go from $\Bad$ to $\Safe$ is equal to $k$.\alain{à prouver}
%
\end{proof}
%
Let us remark that $\uparrow \post^*(q,w)$ is also a computable regular language, but we cannot directly apply previous results on WSTS since pushdown automata are not WSTS for the usual orderings (subword, prefix).
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} for the subword ordering and $\uparrow \post^*$ is computable but context-free grammars are not strongly compatible.

>>>>

\begin{proof}
Recall that resilience is equivalent to  $\Bad \subseteq \pred^*(\Safe)$. For every pushdown automaton $A=(Q,\Sigma,...)$ and every regular language $L \subseteq Q \times \Sigma^*$, the set $\pred^*(L)$ is a computable regular language \cite{DBLP:journals/ipl/BouajjaniEFMRWW00}. Since $\Bad$ and $\Safe$ are both regular, we deduce that
%
%			Moreover, $post^*(\Bad)$ is also a computable regular language \alain{pourquoi ?}   $post^*(L)$ and
 the inclusion $\Bad \subseteq \pred^*(\Safe)$ is decidable and resilience too.
%
The kRP is decidable: let us compute $ \pred^*(\Safe)$ (in polynomial time). If $\Bad \subseteq \pred^*(\Safe)$ then one computes the integer $k_0$ such that the maximum of all minimal pathes that go from $\Bad$ to $\Safe$ is equal to $k$. Then $A=(Q,\Sigma,...)$ is $p$-resilient for all $p \geq k_0$ and it is not $p$-resilient for all $p \leq k_0-1$.

\alain{à prouver la BRP...}
%
\end{proof}
%
Let us remark that $\uparrow \post^*(q,w)$ is also a computable regular language, but we cannot directly apply previous results on WSTS since pushdown automata are not WSTS for the usual orderings (subword, prefix).
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} for the subword ordering and $\uparrow \post^*$ is computable but context-free grammars are not strongly compatible.

### 2023-04-12 definitions.tex
details

In what follows, a downward closed set $D$ is represented by its finite set of ideals 
%		$D=\downarrow D$   $I_D=\{J_1, J_2,...,J_n\}$ 		satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ 
and an upward closed set $U$ is represented by its finite set of minimal elements. \\
% $M_U$ of its  satisfying $U=\uparrow M_U$.

@@

\begin{definition}
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em control states} of $V$, and where $T \subseteq Q \times \mathds{Z}^d \times Q$ will be referred to as the {\em control transitions} of $V$. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
\end{definition}

Subsetquently, $Q \times \N^d$ denotes the set of configurations of $V$.
For every configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every control transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z}$.

>>>>

In what follows, a downward closed set $D$ is represented by its finite set of ideals (or by the minimal elements of its upward-closed complement).
%		$D=\downarrow D$   $I_D=\{J_1, J_2,...,J_n\}$ 		satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ 
and an upward closed set $U$ is represented by its finite set of minimal elements. \\
% $M_U$ of its  satisfying $U=\uparrow M_U$.

@@

\begin{definition}
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control states} of $V$, and where $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control transitions} of $V$. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
\end{definition}

Subsetquently, $Q \times \N^d$ denotes the set of configurations of $V$.
For every configuration $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every control transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z} \geq \textbf{0}$
